\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\usepackage[caption=false, font=footnotesize]{subfig}
\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

\title{CS280.01: Machine Learning\\ Project 1 Report}

\author{Zhixin Piao, Yongfei Liu, Kang Zhou\\
ShanghaiTech University\\
{\tt\small { \{piaozhx, liuyf3, zhoukang\}@shanghaitech.edu.cn}
}}



\maketitle

\begin{abstract}
   Marketing classification is the most common task in machine learning. In this report, we will present the whole pipeline to deal with real marketing case. Our methods can seperate into three main parts, which are data processing, modeling, and explanation respectively. In data processing, we will present some common tricks in machine learning to solve imbalance data, missing value and feautre selection problems. In modeling stage, we use some basic models to do the classification and finally ensemble all the models together to get higher perfermance. We will present some methods to select hyperparameters. At last, we want to give some explanation for our final deicison by diagnosing the weights and anasylis some common features appearing in positive coustomers. Our conclusion can give more hints to our final marketing strategies.
\end{abstract}

\input{dataprocess}
\input{method}
\input{explanation}




{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}
